A Temporal Logic Based Framework for Intrusion Detection

### 2023-08-30 Paper/main.tex
update

\section{EAGLE, a Temporal Monitoring Logic}
According to~\cite{barringer2004program}, EAGLE offers a succinct but powerful set of primitives, essentially supporting recursive parameterized equations, with a minimal/maximal fix-point semantics together with three temporal operators: next-time ($\ocircle$), previous-time ($\odot$), and concatenation ($\cdot$).
\subsection{Basics and syntax}
In EAGLE recursion definitions are supported; in the current framework we can define the following definitions:

\begin{align*}
& \underline{\text{max}}\ \text{Always}(\underline{\text{Form}}\ F) = F \land \bigcirc \text{Always}(F) \\
& \underline{\text{min}}\ \text{Sometime}(\underline{\text{Form}}\ F) = F \lor \bigcirc \text{Sometime}(F) \\
\end{align*}

>>>>

\section{EAGLE, a Temporal Monitoring Logic}
According to~\cite{barringer2004program}, EAGLE offers a succinct but powerful set of primitives, essentially supporting recursive parameterized equations, with a minimal/maximal fix-point semantics together with three temporal operators: next-time ($\ocircle$), previous-time ($\odot$), and concatenation ($\cdot$).
\subsection{Basics and syntax}
In EAGLE recursion definitions are supported; in the current framework we can define the following definitions:
\begin{align*}
\underline{\text{max}}\ \text{Always}(\underline{\text{Form}}\ F) = F \land \bigcirc \text{Always}(F) \\
& \underline{\text{min}}\ \text{Sometime}(\underline{\text{Form}}\ F) = F \lor \bigcirc \text{Sometime}(F) \\
\end{align*}
